Models pretest

### 2022-12-06 Submission/Models_pretest.Rmd
added a 4 model with party ideology and vdem data

>>>>

```{r models lagged ideology, fig.cap="Logistic Regressions Output Lagged Deforestation with Ideology", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}

#table(ama_model$president, ama_model$party)

ideology_vdem <- readRDS("~/Documents/GitHub/amazondef/Submission/V-Dem-CPD-Party-V2.rds") %>% 
dplyr::filter(country_name == "Brazil") %>%
dplyr::select(v2pashname, v2xpa_antiplural, v2xpa_popul, v2pariglef) %>%
tidyr::drop_na() %>%
dplyr::rename(party = v2pashname) %>%
group_by(party) %>%
summarise(anti_pluralism = mean(v2xpa_antiplural),
populism = mean(v2xpa_popul),
left_right = mean(v2pariglef))

ama_model_lag <- dplyr::left_join(ama_model_lag, ideology_vdem)

ama_model2_lag <- dplyr::left_join(ama_model2_lag, ideology_vdem)

# model
model_logit_con_lag <- glm(con_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + populism + anti_pluralism + left_right, family=binomial(link = "logit"),
                       data = ama_model_lag)
model_logit_ei_lag <- glm(EI_vs_all ~ as.factor(location_cat) + election_year +
                        def_year + AAI + populism + anti_pluralism + left_right, family=binomial(link = "logit"),
                      data = ama_model_lag)
model_logit_sd_lag <- glm(SD_vs_all ~ as.factor(location_cat) + election_year +
                        def_year + AAI + populism + anti_pluralism + left_right,
                      family=binomial(link = "logit"), data = ama_model_lag)
model_logit_sov_lag <- glm(sov_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + populism + anti_pluralism + left_right,
                       family=binomial(link = "logit"), data = ama_model_lag)
model_logit_all_lag <- glm(amazon_speech ~ as.factor(location_cat) + election_year +
                         def_year + AAI + populism + anti_pluralism + left_right,
                       family=binomial(link = "logit"), data = ama_model2_lag)

stargazer::stargazer(model_logit_con_lag, model_logit_ei_lag, model_logit_sd_lag,
                     model_logit_sov_lag, model_logit_all_lag, digits = 6,
                     no.space = TRUE,
                     title = "Logistic Regressions with Lagged Year and Party Ideology")
```
